\documentclass[11pt,letterpaper]{article}

% ============================================================
% NSF SBIR Phase I master source:
% Project Summary + Project Description + References Cited
%
% IMPORTANT:
% Research.gov requires these as separate PDF uploads.
% Set exactly ONE switch below to true, compile, and save the PDF.
% ============================================================

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Times-like text and mathematics fonts
\usepackage{newtxtext}
\usepackage{newtxmath}

% Improve text search and copy quality in the PDF
\input{glyphtounicode}
\pdfgentounicode=1

% ============================================================
% Page setup
% ============================================================
\usepackage[
    letterpaper,
    top=1in,
    bottom=1in,
    left=1in,
    right=1in
]{geometry}

% ============================================================
% Mathematics
% Do not load amssymb together with newtxmath
% ============================================================
\usepackage{amsmath}

% ============================================================
% Figures, tables, and layout
% ============================================================
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{float}
\usepackage{xcolor}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

% ============================================================
% Lists
% ============================================================
\usepackage{enumitem}

\setlist[itemize]{
    leftmargin=*,
    itemsep=2pt,
    topsep=3pt,
    parsep=0pt
}

\setlist[enumerate]{
    leftmargin=*,
    itemsep=2pt,
    topsep=3pt,
    parsep=0pt
}

% ============================================================
% Captions
% ============================================================
\usepackage{caption}

\captionsetup{
    font=small,
    labelfont=bf,
    singlelinecheck=false
}

% ============================================================
% Typography and spacing
% ============================================================
\usepackage{microtype}
\usepackage{setspace}

\singlespacing

\setlength{\parindent}{0.25in}
\setlength{\parskip}{0pt}

% ============================================================
% Headings
% ============================================================
\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\Large\bfseries}
  {}
  {0pt}
  {}

\titleformat{\subsection}
  {\normalfont\large\bfseries}
  {}
  {0pt}
  {}

\titleformat{\subsubsection}
  {\normalfont\normalsize\bfseries}
  {}
  {0pt}
  {}

\titlespacing*{\section}
  {0pt}
  {0pt}
  {0pt}

\titlespacing*{\subsection}
  {0pt}
  {2pt}
  {1pt}

\titlespacing*{\subsubsection}
  {0pt}
  {4pt}
  {2pt}

% ============================================================
% Bibliography
% ============================================================
\usepackage[numbers,sort&compress]{natbib}

% ============================================================
% Hyperlinks
% Load near the end of the preamble
% ============================================================
\usepackage[hidelinks]{hyperref}

% ============================================================
% Page style
% ============================================================
\pagestyle{empty}

% ============================================================
% Document
% ============================================================
\begin{document}
\section*{11. Data Management and Sharing Plan}

\subsection*{Data and Materials Expected}
The project may generate benchmark prompts, structured requirements,
reference-design representations, expert annotations, model outputs, evaluation
metrics, software logs, prototype documentation, and controlled test results.
If human participants are included, the project may also generate limited
consented usability or comprehension data.

\subsection*{Formats and Documentation}
Data will be maintained in commonly used structured formats such as CSV, JSON,
plain text, PDF, images, source code, and version-controlled documentation.
Metadata will describe provenance, version, benchmark split, annotation status,
model configuration, and evaluation conditions.

\subsection*{Storage, Security, and Access}
Project data will be stored in access-controlled company systems with secure
authentication, encrypted transmission, role-based permissions, and routine
backup. Access will be limited to authorized project personnel and approved
consultants or partners.

\subsection*{Privacy and Human-Subjects Data}
No personally identifiable information will be collected unless specifically
required by an approved or exempt human-subjects protocol. Any participant data
will be minimized, de-identified where possible, and retained only as necessary
for the approved research purpose.

\subsection*{Sharing and Proprietary Restrictions}
Because the proposed work is intended to produce commercially valuable
software, reference-design structures, safety policies, benchmark assets, and
evaluation methods, some or all project data may be considered proprietary.
Public sharing will be limited to materials that do not compromise company IP,
participant privacy, security, contractual obligations, or commercialization.

\subsection*{Preservation and Reproducibility}
The company will retain the records needed to reproduce Phase I analyses,
including code versions, model configurations, benchmark versions, evaluation
scripts, and summary results, for the period required by applicable NSF and
company record-retention policies.

\end{document}
