\documentclass[11pt,letterpaper]{article}

% ============================================================
% NSF SBIR Phase I master source:
% Project Summary + Project Description + References Cited
%
% IMPORTANT:
% Research.gov requires these as separate PDF uploads.
% Set exactly ONE switch below to true, compile, and save the PDF.
% ============================================================

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Times-like text and mathematics fonts
\usepackage{newtxtext}
\usepackage{newtxmath}

% Improve text search and copy quality in the PDF
\input{glyphtounicode}
\pdfgentounicode=1

% ============================================================
% Page setup
% ============================================================
\usepackage[
    letterpaper,
    top=1in,
    bottom=1in,
    left=1in,
    right=1in
]{geometry}

% ============================================================
% Mathematics
% Do not load amssymb together with newtxmath
% ============================================================
\usepackage{amsmath}

% ============================================================
% Figures, tables, and layout
% ============================================================
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{float}
\usepackage{xcolor}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

% ============================================================
% Lists
% ============================================================
\usepackage{enumitem}

\setlist[itemize]{
    leftmargin=*,
    itemsep=2pt,
    topsep=3pt,
    parsep=0pt
}

\setlist[enumerate]{
    leftmargin=*,
    itemsep=2pt,
    topsep=3pt,
    parsep=0pt
}

% ============================================================
% Captions
% ============================================================
\usepackage{caption}

\captionsetup{
    font=small,
    labelfont=bf,
    singlelinecheck=false
}

% ============================================================
% Typography and spacing
% ============================================================
\usepackage{microtype}
\usepackage{setspace}

\singlespacing

\setlength{\parindent}{0.25in}
\setlength{\parskip}{0pt}

% ============================================================
% Headings
% ============================================================
\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\Large\bfseries}
  {}
  {0pt}
  {}

\titleformat{\subsection}
  {\normalfont\large\bfseries}
  {}
  {0pt}
  {}

\titleformat{\subsubsection}
  {\normalfont\normalsize\bfseries}
  {}
  {0pt}
  {}

\titlespacing*{\section}
  {0pt}
  {0pt}
  {0pt}

\titlespacing*{\subsection}
  {0pt}
  {2pt}
  {1pt}

\titlespacing*{\subsubsection}
  {0pt}
  {4pt}
  {2pt}

% ============================================================
% Bibliography
% ============================================================
\usepackage[numbers,sort&compress]{natbib}

% ============================================================
% Hyperlinks
% Load near the end of the preamble
% ============================================================
\usepackage[hidelinks]{hyperref}

% ============================================================
% Page style
% ============================================================
\pagestyle{empty}

% ============================================================
% Document
% ============================================================
\begin{document}
% ============================================================
% File: sections/main/8_Budget_Justification.tex
% Purpose: NSF SBIR Phase I Budget Justification Template
% Primary owner: Alfredo / Finance Lead
% Technical input and consistency review: Lu
%
% Replace all bracketed placeholders before submission.
% Delete unused sections and rows.
% Ensure that every non-zero Research.gov budget line is justified.
% ============================================================

\section*{Budget Justification}

\noindent
\textbf{Project Title:} [Insert final project title]

\noindent
\textbf{Company:} ALTITUT LLC

\noindent
\textbf{Principal Investigator:} Lu Sun

\noindent
\textbf{Project Period:} [Insert start date] to [Insert end date]

\noindent
\textbf{Total Requested Amount:} \$[Insert total]

\medskip

This Budget Justification explains the costs required to execute the proposed
12-month NSF SBIR Phase I R\&D project. All costs are based on reasonable
company salary records, fringe and indirect-cost practices, vendor estimates,
historical costs, or documented project assumptions. The budget is aligned
with the Phase I objectives, work plan, milestones, experimental protocol, and
personnel responsibilities described in the Project Description.

% ============================================================
\subsection*{A. and B. Personnel}

\subsubsection*{Lu Sun, Principal Investigator}

Lu Sun will devote approximately [insert] person-months to the proposed Phase
I project. Her responsibilities will include:

\begin{itemize}
    \item overall technical and research direction;
    \item uncertainty-aware intent-to-constraint methodology;
    \item clarification-ranking logic;
    \item benchmark and expert-annotation protocol design;
    \item evaluation metrics and go/no-go analysis;
    \item integration of the three Phase I objectives;
    \item coordination of technical, commercial, and partner inputs;
    \item preparation of NSF technical reports and deliverables.
\end{itemize}

Lu Sun's annual salary base is \$[insert]. The requested salary is calculated
as follows:

\[
\$[\text{annual salary}]
\times
\frac{[\text{person-months}]}{12}
=
\$[\text{requested salary}]
\]

\subsubsection*{Mengmeng Wang, Key Personnel}

Mengmeng Wang will devote approximately [insert] person-months to the proposed
Phase I project. Her responsibilities will include:

\begin{itemize}
    \item development and review of low-voltage reference designs;
    \item component, interface, power, and physical-system reasoning;
    \item definition of supported customization ranges;
    \item build/test procedures and expected observations;
    \item identification of known failure modes;
    \item safety-boundary and expert-review criteria;
    \item expert annotation and adjudication of benchmark cases;
    \item technical review of controlled hardware validation.
\end{itemize}

Mengmeng Wang's annual salary base is \$[insert]. The requested salary is
calculated as follows:

\[
\$[\text{annual salary}]
\times
\frac{[\text{person-months}]}{12}
=
\$[\text{requested salary}]
\]

\subsubsection*{Diana [Last Name], [Project Role]}

\textit{Delete this subsection if Diana is not included as Senior/Key
Personnel.}

Diana [Last Name] will devote approximately [insert] person-months to the
proposed Phase I project. Her responsibilities will include:

\begin{itemize}
    \item [Insert responsibility];
    \item [Insert responsibility];
    \item [Insert responsibility];
    \item [Identify specific objective or work-plan task supported].
\end{itemize}

Her annual salary base is \$[insert]. The requested salary is calculated as
follows:

\[
\$[\text{annual salary}]
\times
\frac{[\text{person-months}]}{12}
=
\$[\text{requested salary}]
\]

\subsubsection*{Software / AI Engineering Personnel}

ALTITUT will budget approximately [insert] person-months for software and AI
engineering personnel. These personnel will support:

\begin{itemize}
    \item implementation of the uncertainty-aware research prototype;
    \item structured constraint and reference-design representations;
    \item LLM and retrieval orchestration;
    \item baseline-system implementation;
    \item benchmark execution;
    \item evaluation dashboards and logging;
    \item skill-adaptive guidance generation;
    \item abstention and escalation logic;
    \item secure data handling and internal testing.
\end{itemize}

The requested amount of \$[insert] is based on [insert salary or hourly-rate
assumption and calculation].

\subsubsection*{Research Assistants / Interns}

ALTITUT may use research assistants or interns to support documentation,
benchmark preparation, test-case execution, measurement logging, and
interface testing under senior technical supervision. These personnel will
not have independent authority to approve reference designs, safety
boundaries, or engineering decisions.

The requested amount of \$[insert] is based on [insert number of personnel,
hours or person-months, and rate].

% ============================================================
\subsection*{C. Fringe Benefits}

Fringe benefits are requested at a rate of [insert]\% applied to eligible
salary and wage costs of \$[insert], resulting in total requested fringe
benefits of \$[insert].

The fringe-benefit rate includes [insert applicable components, such as
employer payroll taxes, health benefits, retirement contributions, workers'
compensation, or other company-supported benefits]. The rate is based on
[company payroll records / accounting estimate / approved company practice].

Calculation:

\[
\$[\text{eligible salary base}]
\times
[\text{fringe rate}]
=
\$[\text{requested fringe}]
\]

% ============================================================
\subsection*{D. Equipment}

\textit{If no equipment is requested, use the following statement:}

No equipment costs are requested.

\medskip

\textit{If equipment is requested, replace the sentence above with a
description for each item:}

ALTITUT requests \$[insert] for [insert equipment item]. This item is required
to [describe specific Phase I experimental purpose]. It will support
[identify objective, benchmark, or validation activity]. The estimated cost is
based on [vendor quote, catalog price, or other source]. The item is not
currently available to the company in a form that can support the proposed
R\&D.

Routine office or general-purpose computing equipment is not included unless
its project-specific use and allowability have been confirmed.

% ============================================================
\subsection*{E. Travel}

\textit{If no travel is requested, use the following statement:}

No travel costs are requested.

\medskip

\textit{If travel is requested, replace the sentence above with:}

ALTITUT requests \$[insert] for [number] traveler(s) to travel to
[destination] for [purpose]. The travel will support [customer discovery,
partner coordination, controlled testing, NSF-required meeting, or other
specific purpose].

Estimated costs include:

\begin{itemize}
    \item airfare or mileage: \$[insert];
    \item lodging: [number] nights at \$[insert] per night;
    \item per diem: [number] days at \$[insert] per day;
    \item local transportation: \$[insert];
    \item other allowable travel costs: \$[insert].
\end{itemize}

The total requested travel amount is \$[insert].

% ============================================================
\subsection*{G.1 Materials and Supplies}

ALTITUT requests \$[insert] for materials and supplies needed to build,
adapt, and evaluate the bounded low-voltage physical-computing reference
designs used in Phase I.

The estimated cost includes:

\begin{itemize}
    \item \textbf{Embedded development boards:} \$[insert].
    These boards will support the IoT smart-camera reference platform and
    controlled physical-computing variants.

    \item \textbf{Sensors, cameras, and interface components:} \$[insert].
    These components will support benchmark cases involving sensing,
    interaction, environmental monitoring, and interface adaptation.

    \item \textbf{Power-management and battery components:} \$[insert].
    These components will support testing of runtime, power-budget, heat,
    compatibility, and user-contact constraints.

    \item \textbf{Lighting, display, and actuator components:} \$[insert].
    These components will support controlled creative-hardware variants such
    as wearable lighting, environmental displays, and interactive
    installations.

    \item \textbf{Wiring, connectors, breadboards, and assembly supplies:}
    \$[insert].
    These consumable supplies are required for controlled module reuse,
    modification, testing, and failure-case evaluation.

    \item \textbf{Enclosure and fabrication supplies:} \$[insert].
    These supplies will support physical adaptation, user-contact,
    environmental, weight, and fabrication-boundary cases.

    \item \textbf{Measurement and test supplies:} \$[insert].
    These supplies will support documentation of expected observations,
    failure conditions, and test-step completeness.

    \item \textbf{Other project-specific supplies:} \$[insert].
    [Explain.]
\end{itemize}

The estimates are based on [vendor prices, recent purchases, or other
documented assumptions]. All materials will be used directly for Phase I R\&D
and controlled validation.

% ============================================================
\subsection*{G.3 Consultant Services}

\textit{Delete this section if no consultants are included.}

ALTITUT requests \$[insert] for consultant services.

\subsubsection*{[Consultant Name], [Area of Expertise]}

[Consultant name] will provide expertise in [embedded hardware, electrical
safety, human factors, statistics, commercialization, or another area]. The
consultant will support:

\begin{itemize}
    \item [Insert specific deliverable];
    \item [Insert specific deliverable];
    \item [Insert specific deliverable];
    \item review of relevant Phase I methods, outputs, or decisions.
\end{itemize}

The consultant will work approximately [insert] days/hours at a rate of
\$[insert] per [day/hour], for a total requested amount of \$[insert].

The consultant's expertise is needed because [explain why this expertise is
not fully available among budgeted company personnel]. A commitment letter
will be included if required or appropriate.

% ============================================================
\subsection*{G.4 Computer Services}

ALTITUT requests \$[insert] for computer and software services required to
implement and evaluate the Phase I research prototype.

The requested costs include:

\begin{itemize}
    \item \textbf{Cloud computing:} \$[insert].
    Cloud resources will support development, model execution, benchmark
    evaluation, logging, and prototype hosting. The estimate is based on
    \$[insert] per month for [insert] months.

    \item \textbf{Commercial model and API usage:} \$[insert].
    These costs will support general-purpose LLM baselines, model
    orchestration, controlled repeated runs, and comparison against the
    proposed uncertainty-aware system. The estimate is based on [insert usage
    assumption].

    \item \textbf{Secure data storage and backup:} \$[insert].
    Storage will be used for benchmark prompts, expert annotations,
    reference-design records, system outputs, evaluation results, and versioned
    backups.

    \item \textbf{Specialized software services:} \$[insert].
    [Describe any project-specific software, simulation, design, annotation,
    security, or data service.]

    \item \textbf{Other computer services:} \$[insert].
    [Explain.]
\end{itemize}

The requested services are directly tied to Phase I development and
evaluation and are not routine general business expenses.

% ============================================================
\subsection*{G.5 Subaward(s)}

\textit{If no subaward is included, use the following statement:}

No subaward costs are requested.

\medskip

\textit{If a subaward is included, replace the statement above with:}

ALTITUT requests \$[insert] for a subaward to [institution]. The subawardee
will perform [describe scope]. Major deliverables will include:

\begin{itemize}
    \item [Insert deliverable];
    \item [Insert deliverable];
    \item [Insert deliverable].
\end{itemize}

The subaward is necessary because [explain specialized facilities,
capabilities, participant access, or expertise]. The company will retain
responsibility for overall technical direction, system integration,
commercialization, and the majority of the proposed R\&D, consistent with
applicable SBIR work-share requirements.

A separate subaward budget, Budget Justification, scope of work, and
commitment documentation will be included as required.

% ============================================================
\subsection*{G.6 Other Direct Costs}

\textit{If no other direct costs are requested, use the following statement:}

No other direct costs are requested.

\medskip

\textit{If other direct costs are requested, replace the statement above:}

ALTITUT requests \$[insert] for [cost item]. The amount is calculated as
[insert calculation]. This cost is necessary to [explain direct relationship
to the Phase I R\&D].

% ============================================================
\subsection*{I. Indirect Costs}

ALTITUT requests indirect costs of \$[insert], calculated using an indirect
cost rate of [insert]\% applied to an eligible base of \$[insert].

Calculation:

\[
\$[\text{eligible base}]
\times
[\text{indirect rate}]
=
\$[\text{requested indirect costs}]
\]

The rate is based on [negotiated indirect-cost rate / de minimis rate /
company accounting methodology / other approved basis]. The company will
maintain supporting accounting documentation for the selected rate and base.

% ============================================================
\subsection*{K. Fee}

ALTITUT requests a fee of \$[insert]. The requested fee is calculated as
[insert calculation] and does not exceed the applicable limitation under the
active NSF SBIR Phase I solicitation.

The fee will support the company's continued commercial development and
organizational sustainability associated with advancing the proposed
innovation beyond the Phase I R\&D period.

% ============================================================
\subsection*{Budget Alignment with Phase I Objectives}

The budget is structured to support the three proposed Phase I objectives:

\begin{table}[htbp]
\centering
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{
    p{0.19\textwidth}
    p{0.25\textwidth}
    X
}
\toprule
\textbf{Objective} &
\textbf{Principal Budget Categories} &
\textbf{Budget Relationship} \\
\midrule

Objective 1:
Intent-to-Constraint Translation &
PI effort; software/AI personnel; cloud and model services; expert annotation &
Supports schema development, uncertainty representation, clarification
ranking, benchmark construction, baseline evaluation, and quantitative
analysis. \\

Objective 2:
Bounded Reference-Design Adaptation &
PI and engineering effort; hardware materials; consultant support if used;
reference-design documentation &
Supports reference-design schemas, controlled hardware variants, adaptation
classification, interface and safety-conflict cases, and expert validation. \\

Objective 3:
Skill-Adaptive Build/Test Guidance and Abstention &
PI and software effort; testing supplies; cloud/model services; user or expert
evaluation support &
Supports guidance generation, test sequencing, evidence labels,
troubleshooting, abstention calibration, and integrated evaluation. \\

Integrated Validation &
All personnel categories; cloud computing; measurement supplies; statistical
or technical consultant support if used &
Supports held-out benchmark evaluation, failure analysis, expert review,
prototype integration, and the final Phase I feasibility report. \\

\bottomrule
\end{tabularx}
\end{table}

% ============================================================
\subsection*{Final Budget-Justification Review}

Before submission, confirm:

\begin{itemize}
    \item[$\square$] Every non-zero Research.gov line is explained.
    \item[$\square$] Every calculation is shown or reproducible.
    \item[$\square$] Personnel effort matches the Project Description.
    \item[$\square$] Salary information matches company records.
    \item[$\square$] Fringe and indirect-cost rates have documented bases.
    \item[$\square$] Materials align with the benchmark and hardware plan.
    \item[$\square$] Computing costs align with the model and evaluation plan.
    \item[$\square$] Consultant costs match commitment letters.
    \item[$\square$] Subaward information matches all separate documents.
    \item[$\square$] The requested fee complies with the active solicitation.
    \item[$\square$] The total matches the Research.gov budget exactly.
\end{itemize}

\end{document}
